Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures

### 2025-05-18 CCGRID Presentation/main.tex
corected Res formula also in the presentation
added pauses

    \begin{itemize}
        \item Large applications represented as DAG-shaped workflows
        \item Heterogeneous execution environment with limited memories
         \begin{itemize}
                  \item Exceed memory = expensive or even fatal
        \end{itemize}
        \item Execute the workflow fast
    \end{itemize}

@@

            %\caption{Caption }
        \end{figure}
    \column{0.39\textwidth}
    \only<1>{
     \begin{figure}
            \centering
            \includegraphics[scale=0.3]{diagrams/images/CCGrid-muffin.png}

            %\caption{Caption }
        \end{figure}
    }
    \only<2>{
     \begin{figure}
            \centering
            \includegraphics[scale=0.3]{diagrams/images/CCgrid-muffin-no.png}

@@

    ~~~~~~~~~~~~~~~~~

@@

@@

             \uncover<3,4>{
             \item Keep track of ready times on each
                  \begin{itemize}
                      \item Communication channel: $rt_{j,j'}$
                      \item Communication buffer:  $rt_j$
                  \end{itemize}  
                  }
         \end{itemize}

@@

@@

@@

\begin{frame}[t]
    \frametitle{Final Assignment}

    Final assignment to processor

    \begin{itemize}
        \item Evict files that need to be evicted from memory,
        \begin{itemize}
            \item  remove them from pending memory and add to communication buffer
            \item reduce buffers sizes accordingly
        \end{itemize}
        \item New $availM_j$: - eviction, - incoming files, + outgoing files
        \item For each predecessor on another processor $j'$: ready time on communication buffer $rt_{j, j'}$

@@

    \vspace{-0.8cm}
    \begin{figure}    
        \centering
         \hskip -0.5cm
        \includegraphics[scale=0.38]{diagrams/images/success-rates-large2.png}
        % \caption{Makespans of HomPart in comparison to HetPart1.}
    \end{figure}

@@

    \begin{tikzpicture}[remember picture, overlay]
            \node[
                fill=white,
                draw=black,
                rounded corners,
                minimum width=4cm,
                minimum height=1.5cm,
                align=center
            ] at ([xshift=-5cm,yshift=-3.8cm]current page.north east)
            {HEFTM-* makespans valid, HEFT not \\ HEFTM-BL and BLC : 10 - 35\% worse \\ HEFTM-MM makespans 40\% to 2x worse};
        \end{tikzpicture}

@@

      \vspace{-0.3cm}
        \begin{figure}
            \centering
            \hskip -0.5cm
            \includegraphics[scale=1.25]{diagrams/images/success-rates-tiny.png}
           % \caption{Makespans of HomPart in comparison to HetPart1.}
        \end{figure}

@@

    \begin{tikzpicture}[remember picture, overlay]
        \node[
            fill=white,
            draw=black,
            rounded corners,
            minimum width=4cm,
            minimum height=1.5cm,
            align=center
        ] at ([xshift=-5.0cm,yshift=-4.5cm]current page.north east)
        {Most makespans invalid, \\
        even by HEFTM-BL and HEFTM-BLC; \\ HEFTM-MM makespans the only valid ones };
    \end{tikzpicture}
   \end{frame}

@@

    \begin{tikzpicture}[remember picture, overlay]
        \node[
            fill=white,
            draw=black,
            rounded corners,
            minimum width=4.8cm,
            minimum height=1.7cm,
            align=center
        ] at ([xshift=-4.5cm,yshift=-4.5cm]current page.north east)
        {Runtimes from 1/100 of seconds to minutes\\
         HEFTM-MM has longest runtimes\\
         Computation of optimal traversal costly};
    \end{tikzpicture}

@@

@@

\begin{itemize}
    \item Extend an influential predecessor (HEFT)
    \item Memory-aware, communicate over communication buffers
    \item Valid makespans, only 10-35\% worse than invalid HEFT makespans
    \item HEFT-\textbf{MM} proves unique resilience in memory-constrained scenario
\end{itemize}

\pause
    \begin{table}[ht]
        \centering
        \setlength{\tabcolsep}{12pt} % adjust horizontal padding between columns
        \renewcommand{\arraystretch}{1.3} % increase row height for readability
        \begin{tabular}{|p{6.5cm}|p{2.5cm}|}
            \hline
            \textbf{Scenario} & \textbf{Winner} \\
            \hline
            Memory very constrained & HEFT-\textbf{MM} \\
            Memory somewhat constrained, need smallest makespan & HEFTM-\textbf{BL} \\
            Need balance, willing to trade (very little) makespan for less memory requirement & HEFTM-\textbf{BLC} \\
            Lots of memory, need smallest makespan & \only<1>{HEFT?} \only<2> {\sout{HEFT} ~~~~~~~ HEFTM-\textbf{BL}} \\
            \hline
        \end{tabular}
    \end{table}

>>>>

    \begin{itemize}
        \item Large applications represented as DAG-shaped workflows
        \uncover<2,3>{
        \item Heterogeneous execution environment with limited memories
         \begin{itemize}
                  \item Exceed memory = expensive or even fatal
        \end{itemize}
        \item Execute the workflow fast
         }
    \end{itemize}

@@

            %\caption{Caption }
        \end{figure}
    \column{0.39\textwidth}
    \only<2>{
     \begin{figure}
            \centering
            \includegraphics[scale=0.3]{diagrams/images/CCgrid-muffin.png}

            %\caption{Caption }
        \end{figure}
    }
    \only<3>{
     \begin{figure}
            \centering
            \includegraphics[scale=0.3]{diagrams/images/CCgrid-muffin-no.png}

@@

    \pause
    ~~~~~~~~~~~~~~~~~

@@

        \pause

@@

             \uncover<3,4>{
             \item Keep track of ready times on each
                  \begin{itemize}
                      \item Communication channel: $rt_{j,j'}$
                      \item Processor:  $rt_j$
                  \end{itemize}  
                  }
         \end{itemize}

@@

       \begin{figure}
            \centering
            \includegraphics[width=.8\textwidth]{diagrams/images/Res-formula}
        \end{figure}
  \end{itemize}

@@

     \vspace{-0.6cm}
       % --- Foreground content (text appears over image) ---
    \begin{itemize}
        \item Start after all communications have finished
        \pause
        \begin{figure}
            \centering
            \hskip -5.5cm
            \includegraphics[width=.6\textwidth]{diagrams/images/formula-starttime-paperwithrts.png}
        \end{figure}

@@

\begin{frame}[t]
    \frametitle{Final Assignment}
    \framesubtitle{Final assignment to processor}

    Previously - no change in the execution environment.
    \begin{itemize}
        \item Apply all tentative memory-related changes
        \item Assign the task
        \pause
        \item $availM_j$ after exectution: - eviction, - incoming files, + outgoing files
        \item For each predecessor on another processor $j'$: ready time on communication buffer $rt_{j, j'}$
    \end{itemize}

    \begin{center}
        \includegraphics[scale=0.4]{diagrams/images/mem-after}
    \end{center}

@@

    \vspace{-0.8cm}
    \begin{figure}    
        \centering
         \hskip -0.5cm
        \includegraphics[scale=0.36]{diagrams/images/success-rates-large2.png}
        % \caption{Makespans of HomPart in comparison to HetPart1.}
    \end{figure}

@@

    \begin{tikzpicture}[remember picture, overlay]
            \node[
                fill=white,
                draw=black,
                rounded corners,
                minimum width=4cm,
                minimum height=1.5cm,
                align=center
            ] at ([xshift=-5cm,yshift=-4.2cm]current page.north east)
            {HEFTM-* makespans valid, HEFT not \\ HEFTM-BL and BLC : 10 - 35\% worse \\ HEFTM-MM makespans 40\% to 2x worse};
        \end{tikzpicture}

@@

      \vspace{-0.3cm}
        \begin{figure}
            \centering
            \hskip -0.3cm
            \includegraphics[scale=1.2]{diagrams/images/success-rates-tiny.png}
           % \caption{Makespans of HomPart in comparison to HetPart1.}
        \end{figure}

@@

    \begin{tikzpicture}[remember picture, overlay]
        \node[
            fill=white,
            draw=black,
            rounded corners,
            minimum width=4cm,
            minimum height=1.5cm,
            align=center
        ] at ([xshift=-4.0cm,yshift=-5.5cm]current page.north east)
        {Most makespans invalid, \\
        even by HEFTM-BL and HEFTM-BLC; \\ HEFTM-MM makespans the only valid ones };
    \end{tikzpicture}
   \end{frame}

@@

    \begin{tikzpicture}[remember picture, overlay]
        \node[
            fill=white,
            draw=black,
            rounded corners,
            minimum width=4.8cm,
            minimum height=1.7cm,
            align=center
        ] at ([xshift=-4.5cm,yshift=-6.0cm]current page.north east)
        {Runtimes from 1/100 of seconds to minutes\\
         HEFTM-MM has longest runtimes\\
         Computation of optimal traversal costly};
    \end{tikzpicture}

@@

    \vspace{-1cm}

    Compare makespans of recomputed schedules vs following the original

    ~~~~

@@

\begin{itemize}
    \item Extend an influential predecessor (HEFT)
    \item Memory-aware, communicate over communication buffers
    \item Valid makespans, only 10-35\% worse than invalid HEFT makespans
    \item HEFTM-\textbf{MM} proves unique resilience in memory-constrained scenario
\end{itemize}

\pause
    \begin{table}[ht]
        \centering
        \setlength{\tabcolsep}{12pt} % adjust horizontal padding between columns
        \renewcommand{\arraystretch}{1.3} % increase row height for readability
        \begin{tabular}{|p{6.5cm}|p{2.5cm}|}
            \hline
            \textbf{Scenario} & \textbf{Winner} \\
            \hline
            Memory very constrained & HEFTM-\textbf{MM} \\
            Memory somewhat constrained, need smallest makespan & HEFTM-\textbf{BL} \\
            Need balance, willing to trade (very little) makespan for less memory requirement & HEFTM-\textbf{BLC} \\
            Lots of memory, need smallest makespan & \only<1>{HEFT?} \only<2> {\sout{HEFT} ~~~~~~~ HEFTM-\textbf{BL}} \\
            \hline
        \end{tabular}
    \end{table}
